---
title: "Training one"
author: "Victor Mandela"
date: "6/15/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction basics

1. create a github account... future 

2. most of the data is going to be from

https://archive.ics.uci.edu/ml/datasets.php

3. Data cleaning process. 

4. give questions and comments. 


## steps in data management

- Access the data -  SQL, dplyr


```{r}
#load the packages
library(tidyverse)
library(readxl)

#read in the data in excel
data <- read_xlsx("AirQualityUCI.xlsx")

#explore
glimpse(data)

```

#data types

Text data

Integer

Decimals

Binary

categorical data

Dates

library(assertive)

library(janitor)  #cleaning data

### Process of data

1. Access data

2. Explore and process the data

3. Extract insight 

4. report insights


```{r}
clean_data <- janitor::clean_names(data)
```



```{r}
library(skimr)   #used to compute summary for all variables

skimr::skim(clean_data)
```














